\documentclass[a4paper,12pt]{article}

\include{cv-commands}

\begin{document}

\setmainfont

%% No hyphenation
%% \hyphenchar\font=-1

\header
{Jinu P R}
{Development Engineer}
{Age: 24 years old\\
Email: jinu.p.r@gmail.com\\
Tel: \smcp{(+91) 8122762134}}
\largeskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumesummary}{Summary}
\begin{itemize}
  \item Have been developing highly scalable, available \& fault-tolerant platforms on the cloud from February 2012.
  \item Worked in popular opensource Virtualization technologies.
  \item Worked on end-to-end Web development for K7 Tracker from January 2013.
\end{itemize}
\end{resumesummary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Formation}
\resumeitem{2007-2011}{B-Tech in Information Technology from Government Engineering College Palakkad, University of Calicut, Kerala.} \\

\resumeitem{2005-2007}{Higher Secondary Education in Bio-Science from St.clare’s CGHSS, Thrissur, Kerala.} 
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Technical Skills}

\resumeitem{Technologies}{OpenCV, LXC, Xen, OpenVZ, Pylons,Web2py, Infrastructure as a Service.}
\largeskip

\resumeitem{Operating Systems}{GNU/Linux, Mac OSX.}
\largeskip

\resumeitem{Languages}{Python, C, Javascript,NodeJS}
\largeskip

\resumeitem{Databases}{MySQL,riak}
\largeskip

\resumeitem{Version Control}{Subversion,Exposure to Mercurial and git}
\largeskip

\resumeitem{Cloud Platforms}{Google App Engine}
\largeskip

\resumeitem{Recent Interests}{Django}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Professional Experience}

\resumeitem{From Feb 2012}{Development Engineer at K7 Computing Private Limited, Chennai.\vspace{0mm}
  \begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
    \item Integrated linux containers into StackIron (A virtualization platform).
    \item Worked on the ARM server solution from K7(TrueCore).
    \item Wrote Unit Tests for EggPlug (A NAS and Cloud Storage Device).
    \item Worked end-to-end on K7 Tracker UI and Server.
    
  \end{itemize}}
  \largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{StackIron,\\ Hypervisor Manager}{StackIron is a virtualization platform. StackIron provides a unified interface to man-
age all opensource hypervisors. A pure python implementation for which we developed
our own development framework and billing solution. It comes integrated with third
party billing solutions like WHMCS as well. All basic functionalities like backup, tem-
platization, migration, SAN and local storage management work seamlessly across all
hypervisors.StackIron provides fine grained user control and allows various levels of
user configurations at runtime. StackIron has an optional VLAN and bonding func-
tionality along with Basic Firewall and traffic controlling.}
\largeskip
\resumeitem{K7 Tracker,\\ Security Tracking Software}{K7 Tracker is an invisible software security application that traces the location of missing
laptops for recovery. It is a light weight application that will help you track and find your
laptop if it ever gets stolen. K7 Tracker provides a method for mitigating this risk. This
tracking system send, over the Internet, updates regarding the current location of the device
to a remotely administered repository. If the device is lost or stolen, but maintains Internet
connectivity and unmodified software, the tracking system can keep tabs on the current
whereabouts of the device. This data could prove invaluable when the appropriate authorities
attempt to recover the device}
\largeskip


\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Personal Projects}

\resumeitem{Eye Tracking Driven Virtual Computer Mouse}{A camera mouse application was developed in C(using OpenCV) that tracks human
body movements in video from webcam to manipulate virtual computer pointing
devices like mouse.}
\largeskip

\resumeitem{OpenCV Particle segregation}{An application was developed in C (using OpenCV) to classify objects in an image
based on their size and shape.}
\largeskip
\resumeitem{Design of a toy Unix shell}{A small unix shell was implemented in C with support for redirection and piping.}
\largeskip

\resumeitem{Avl Tree Implementation}{An Avl tree datastructure was implemented in C.}
\largeskip

\resumeitem{Bloom Filter Implementation}{A probabilistic datastructure, Bloom Filter was implemented in C.}
\largeskip

\resumeitem{Visualizing graph vertex
coloring using NodeJS and HTML5 Canvas}{A simple program was written to visualize graph vertex coloring using NodeJS and
HTML5 canvas.}
\largeskip


\resumeitem{A Google App Engine based framework for graph algorithm visualization}{An application was developed in Python(running on Google App Engine) to visualize
the graph vertex colouring algorithm.}
\largeskip

\resumeitem{A Google App Engine Based
URL Shortener}{A simple webapp was developed in Python using Google App Engine/python to
shorten URL’s.}
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\begin{resumeblock}{Publications}

%%\resumeitem{Linux For You,\\ October 2009}{\emph{The New Scheduler on the Block, Dedicated to Desktops}: An article about Brain Fuck Scheduler (BFS) for Linux written by famous Linux Kernel hacker Con Kolivas.}
%%\largeskip

%%\resumeitem{ILUG-Cochin,\\ August 2008}{\emph{Custom Kernel Compilation - Ubuntu way}: A HOWTO on compiling custom kernel sources on Ubuntu published on ILUG-Cochin website.}
%%\largeskip

%%\resumeitem{ILUG-Cochin,\\ August 2008}{\emph{Remastering Ubuntu}: A HOWTO on building custom Ubuntu distributions using Reconstructor.}
%%\largeskip

%%\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\begin{resumeblock}{Awards \& Honours}

%%\resumeitem{2011}{Excellence in Software Development, K7 Computing Private Limited.}
%%\shortskip

%%\resumeitem{2008}{Best Project, Jyothi Engineering College.}
%%\shortskip

%%\resumeitem{2002}{Best Student Award, Edakkattuvayal Grama Panchayat, Kerala.}
%%\largeskip

%%\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Online Profiles}

\resumeitem{Blog}{https://jinurajan.wordpress.com}
\shortskip

\resumeitem{Code Repository}{https://bitbucket.org/jinurajan, https://github.com/jinurajan}
\shortskip

\resumeitem{LinkedIn}{http://www.linkedin.com/in/jinuprajan}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{interestsblock}{Interests \& Activities}
	\interest{idea}{Learning new technologies} &
	\interest{gnu}{Free Software Movement}\\
	&\\
	\interest{hack}{Solving problems} &
\end{interestsblock}

\end{document}
